A practical guide to Digital Micro-mirror Devices (DMDs) for wavefront shaping

### 2023-11-21 paper/main.tex

@@

In the supplementary materials~\cite{}, we present an animation illustrating the dynamic pattern.
In off-axis holography,
the local transverse displacement of the fringes
is directly proportional to the phase,
with a displacement equivalent to the period of the fringes corresponding to $2\pi$~\cite{Cuche2000spatial}.
This permits us to estimate the fluctuation in phase over time at a given position of the output plane.
As illustrated in Fig.~\ref{fig:phase_vibrations} (depicted by the red curve),
the phase varies rapidly over time,
a fluctuation attributed to the rapid mechanical vibrations transmitted by the board.\\

>>>>

\subsection{Dispersion}

DMDs are composed of metallic small mirrors,
the response of which is minimally affected by wavelength changes.
This is particularly advantageous for broadband applications requiring amplitude modulation
and operating on a plane conjugated to the DMD's surface.
This is the case for the originally intended application of video projection.
However, for wavefront-shaping applications,
it is typically required to select a specific diffraction order
to acheive phase or complex modulation~\cite{lee1979binary,Gutierrez2024DMD}.
Under such circumstances,
the wavelength-dependency of the diffraction effect becomes important.
The blazed number, denoted by $\mu$ (according to Eq.(\ref{eq:blazed_number})),
scales inversely with the wavelength.
Fig.~\ref{fig:dispersion} shows the blazed number $\mu$
as a function of the wavelength for two pixel pitches $d=7.6$\textmu m and $d=10.8$\textmu m,
with an incident angle of $\alpha' = 20^\circ$.
Within the visible spectrum, $\mu$ fluctuates between $0$ to $1$ over a typical range of roughly 100 nm.\\

\begin{figure}[ht]
  \centering
  \includegraphics[width = 0.75\textwidth]{images/blazing_number_VS_wavelength.pdf}
  \caption{
    \textbf{Dispersion of the diffraction effect.}
    Blazing number $\mu$ (Eq.(\ref{eq:blazed_number})) as a function of the incident wavelength
    for an incident angle $\alpha' = 20^\circ$
    and a pixel pitch of $d=7.6$\textmu m (blue curve)
    and $d=10.8$\textmu m (dashed black curve).
  }
  \label{fig:dispersion}
\end{figure}

@@

In the supplementary materials~\cite{SI}, we present an animation illustrating the dynamic pattern.
In off-axis holography,
the local transverse displacement of the fringes
is directly proportional to the phase,
with a displacement equivalent to the period of the fringes corresponding to $2\pi$~\cite{Cuche2000spatial}.
This permits us to estimate the fluctuation in phase over time at a given position of the output plane.
As illustrated in Fig.~\ref{fig:phase_vibrations} (depicted by the red curve),
the phase varies rapidly over time,
a fluctuation attributed to the rapid mechanical vibrations transmitted by the board.\\
